---
# IMPORTANT: Change settings here, but DO NOT change the spacing.
# Remove comments and add values where applicable.
# The descriptions below should be self-explanatory

#title: "Helping You Write Academic Papers in R using Texevier"
#subtitle: "This will appear as Right Header"

documentclass: "elsarticle"

# --------- Thesis title (Optional - set to FALSE by default).
# You can move the details below around as you please.
Thesis_FP: TRUE
Entry1: "Investigating Instrument Variables: Income and Ability"
Entry2: "\\textbf{Cassandra Pengelly}" # textbf for bold
Entry3: "20346212"
Uni_Logo: Tex/Logo.png # Place a logo in the indicated location (from your root, e.g. defaults to ~/Tex/Logo.png) and uncomment this line. Leave uncommented for no image
Logo_width: 0.3 # If using a logo - use this to set width (size) of image
Entry4: "Econometrics 871: Cross Section Project"
Entry5: "Stellenbosch University"
Entry6: July 2021
# Entry7:
# Entry8:

# --------- Front Page
# Comment: ----- Follow this pattern for up to 5 authors
# AddTitle: TRUE # Use FALSE when submitting to peer reviewed platform. This will remove author names.
# Author1: "Nico Katzke^[__Contributions:__  \\newline _The authors would like to thank no institution for money donated to this project. Thank you sincerely._]"  # First Author - note the thanks message displayed as an italic footnote of first page.
# Ref1: "Prescient Securities, Cape Town, South Africa" # First Author's Affiliation
# Email1: "nfkatzke\\@gmail.com" # First Author's Email address
# 
# Author2: "John Smith"
# Ref2: "Some other Institution, Cape Town, South Africa"
# Email2: "John\\@gmail.com"
# CommonAffiliation_12: TRUE # If Author 1 and 2 have a common affiliation. Works with _13, _23, etc.
# 
# Author3: "John Doe"
# Email3: "Joe\\@gmail.com"

# CorrespAuthor_1: TRUE  # If corresponding author is author 3, e.g., use CorrespAuthor_3: TRUE
# 
# # Comment out below to remove both. JEL Codes only given if keywords also given.
# keywords: "Multivariate GARCH \\sep Kalman Filter \\sep Copula" # Use \\sep to separate
# JELCodes: "L250 \\sep L100"

# ----- Manage headers and footers:
#BottomLFooter: $Title$
#BottomCFooter:
#TopLHeader: \leftmark # Adds section name at topleft. Remove comment to add it.
BottomRFooter: "\\footnotesize Page \\thepage" # Add a '#' before this line to remove footer.
addtoprule: TRUE
addfootrule: TRUE               # Use if footers added. Add '#' to remove line.

# --------- page margins:
margin: 2.3 # Sides
bottom: 2 # bottom
top: 2.5 # Top
HardSet_layout: TRUE # Hard-set the spacing of words in your document. This will stop LaTeX squashing text to fit on pages, e.g.
# This is done by hard-setting the spacing dimensions. Set to FALSE if you want LaTeX to optimize this for your paper.

# --------- Line numbers
linenumbers: FALSE # Used when submitting to journal

# ---------- References settings:
# You can download cls format here: https://www.zotero.org/ - simply search for your institution. You can also edit and save cls formats here: https://editor.citationstyles.org/about/
# Hit download, store it in Tex/ folder, and change reference below - easy.
bibliography: Tex/ref.bib       # Do not edit: Keep this naming convention and location.
csl: Tex/harvard-stellenbosch-university.csl # referencing format used.
# By default, the bibliography only displays the cited references. If you want to change this, you can comment out one of the following:
#nocite: '@*' # Add all items in bibliography, whether cited or not
# nocite: |  # add specific references that aren't cited
#  @grinold2000
#  @Someoneelse2010

# ---------- General:
RemovePreprintSubmittedTo: TRUE  # Removes the 'preprint submitted to...' at bottom of titlepage
Journal: "Journal of Finance"   # Journal that the paper will be submitting to, if RemovePreprintSubmittedTo is set to TRUE.
toc: FALSE                       # Add a table of contents
numbersections: TRUE             # Should sections (and thus figures and tables) be numbered?
fontsize: 11pt                  # Set fontsize
linestretch: 1.2                # Set distance between lines.
link-citations: TRUE            # This creates dynamic links to the papers in reference list.

### Adding additional latex packages:
# header-includes:
#    - \usepackage{colortbl} # Add additional packages here.

output:
  pdf_document:
    keep_tex: TRUE
    template: Tex/TexDefault.txt
    fig_width: 3.5 # Adjust default figure sizes. This can also be done in the chunks of the text.
    fig_height: 3.5
abstract: |
  Abstract to be written here. The abstract should not be too long and should provide the reader with a good understanding what you are writing about. Academic papers are not like novels where you keep the reader in suspense. To be effective in getting others to read your paper, be as open and concise about your findings here as possible. Ideally, upon reading your abstract, the reader should feel he / she must read your paper in entirety.
---

<!-- First: Set your default preferences for chunk options: -->

<!-- If you want a chunk's code to be printed, set echo = TRUE. message = FALSE stops R printing ugly package loading details in your final paper too. I also suggest setting warning = FALSE and checking for warnings in R, else you might find ugly warnings in your paper. -->

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, fig.width = 6, fig.height = 5, fig.pos="H", fig.pos = 'H')
# Note: echo = FALSE implies the code is executed, but not printed in your pdf.
# warning and message = FALSE implies ugly messages and warnings are removed from your pdf.
# These should be picked up when you execute the command chunks (code sections below) in your rmd, not printed in your paper!

# Lets load in example data, and see how this can be stored and later called from your 'data' folder.
if(!require("tidyverse")) install.packages("tidyverse")
library(tidyverse)


# Notice that as you are working in a .Rproj file (I am assuming you are) - the relative paths of your directories start at your specified root.
# This means that when working in a .Rproj file, you never need to use getwd() - it is assumed as your base root automatically.


```


<!-- ############################## -->
<!-- # Start Writing here: -->
<!-- ############################## -->

# Introduction \label{Introduction}

You may suggest any application using one or a combination of techniques that we have learnt
in this course.
You should NOT write an extensive essay about the topic of interest, nor should you conduct
an extensive literature review behind it: you should only reference articles that support the
motivation for your econometric strategy (in the quest of finding a causal interpretation of a
relationship that you are modeling).
Provide descriptive statistics and graphs to aid in your discussion.
The assignment should be between 3-6 pages, including your tables and figures.

You are required to go beyond simply estimating and presenting your results, but to convince
the reader of their robustness by presenting alternative specifications. You should apply
different estimators and specifications where possible.
Discuss the shortcomings of the estimators in obtaining a causal effect and argue why your
strategy is the best available to obtain a causal effect that satisfies relevant assumptions.

Determine an effect of interest and find instrumental variables to estimate it
causally. If possible, use more than one instrument. Given the LATE
assumptions, try and explain why your results differ and which is likely to
represent the causal effect you are looking for. Conduct sufficient specification
tests to establish whether you are overidentifying your instrument set or whether
the IVs shift the estimates enough to indicate that OLS would be inconsistent.


Writing in Rmarkdown is surprizingly easy - see [this website](https://www.rstudio.com/wp-content/uploads/2015/03/rmarkdown-reference.pdf) cheatsheet for a summary on writing Rmd writing tips.

# Data \label{data}

mention survey design for NIDS

# Methodology \label{meth}
This project makes use of 4 different instrument variables: fathers occupation, mothers occupation, mothers education and fathers education

# Results \label{results}

```{r, results = 'asis'}
library(haven)
library(ivreg)
install.packages("modelsummary")
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
data <- read_dta("data/Adult_W5_Anon_V1.0.0.dta")
df1 <- reg1_clean(data)


df2 <- reg2_clean(data)
lm1 <-lm(income ~ age+ age2+ school+tertiary, dfiv)
lm2 <-lm(income ~ age+ age2+ school+tertiary + race + gender, df2)
summary(lm2)

dfiv <- iv1_clean(data)
iv1 <- ivreg(income ~ age + age2 | school + tertiary |
  father_schl + father_tert, data = dfiv)
summary(iv)


if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(df, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(income ~ age)
#lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, iv1,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
font_size(htab) <- 12

# Now simply call the table:
htab

```



<!-- The following is a code chunk. It must have its own unique name (after the r), or no name. After the comma follows commands for R which are self-explanatory. By default, the code and messages will not be printed in your pdf, just the output: -->

```{r Income,  warning =  FALSE, fig.align = 'center', fig.cap = "Income and Education Relationship \\label{Figure1}", fig.ext = 'png', fig.height = 3, fig.width = 6}

  # This is just a random plot to show you a plot. This is done if the getwd() does not point to your Template's directory.
  # Set WD below to your project's working directory.
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
dfplot <- plot_eduInc(data) 

library(ggplot2)
  g <-
  ggplot(data = dfplot,aes(x = education, y = income)) +
  geom_point() +
    stat_smooth(method = "lm",
        col = "#C42126",
        se = FALSE,
        size = 1) +
  theme_bw() +
  # theme(legend.position = "none") +
  theme(plot.title = element_text(size = 10)) +
  theme(axis.title = element_text(size = 10),
        axis.title.x = element_text()) +
  labs(y = "Income", x = "Education", title = "Income and Education Relationship")

g

```



```{r Figure2, include = FALSE, warning =  FALSE, fig.align = 'center', fig.cap = "Caption Here \\label{Figure2}", fig.height = 3, fig.width = 6, dev = 'png'}



```

To reference the plot above, add a ``\\label'' after the caption in the chunk heading, as done above. Then reference the plot as such: As can be seen, Figures \ref{Figure1}  and \ref{Figure2} are excellent, with Figure \ref{Figure2} being particularly aesthetically pleasing due to its device setting of Tikz. The nice thing now is that it correctly numbers all your figures (and sections or tables) and will update if it moves. The links are also dynamic.

I very strongly suggest using ggplot2 (ideally in combination with dplyr) using the ggtheme package to change the themes of your figures.


# Splitting a page




#  Methodology \label{Meth}

## Subsection
Ideally do not overuse subsections. It equates to bad writing.^[This is an example of a footnote by the way. Something that should also not be overused.]




# Results

Tables can be included as follows. Use the _xtable_ (or kable) package for tables. Table placement = H implies Latex tries to place the table Here, and not on a new page (there are, however, very many ways to skin this cat. Luckily there are many forums online!).


```{r ShortTable, results = 'asis'}

library(xtable)
data <- mtcars[1:5,] %>% tibble::as_tibble()

table <- xtable(data, caption = "Short Table Example \\label{tab1}")
  print.xtable(table,
             # tabular.environment = "longtable",
             floating = TRUE,
             table.placement = 'H',
             # scalebox = 0.3,
             comment = FALSE,
             caption.placement = 'bottom'
             )

```

To reference calculations __in text__, _do this:_ From table \ref{tab1} we see the average value of mpg is `r mean(mtcars[1:5,]$mpg)`.

Including tables that span across pages, use the following (note that I add below the table: ``continue on the next page''). This is a neat way of splitting your table across a page.

Use the following default settings to build your own possibly long tables. Note that the following will fit on one page if it can, but cleanly spreads over multiple pages:

```{r LongTable, results = 'asis'}

library(xtable)

data = mtcars %>% tibble::as_tibble()
  addtorow          <- list()
  addtorow$pos      <- list()
  addtorow$pos[[1]] <- c(0)
  addtorow$command  <- c(paste("\\hline \n",
                               "\\endhead \n",
                               "\\hline \n",
                               "{\\footnotesize Continued on next page} \n",
                               "\\endfoot \n",
                               "\\endlastfoot \n",sep=""))
table <- xtable(data, caption = "Long Table Example")
  print.xtable(table,
             tabular.environment = "longtable",
             floating = FALSE, # Leave this as is.
             table.placement = 'H', # Leave this as is.
             booktabs = T, # Aesthetics
             include.rownames = FALSE,  # Typically you don't want this in a table.
             add.to.row = addtorow, # For adding the Continued on next page part...
             comment = FALSE,
             caption.placement = 'top',  # Where do you want the caption?
             size="\\fontsize{12pt}{13pt}\\selectfont"  # Size of text in table..
             )
# See https://cran.r-project.org/web/packages/xtable/vignettes/xtableGallery.pdf for table inspiration
```

\hfill

<!-- hfill can be used to create a space, like here between text and table. -->


## Huxtable

Huxtable is a very nice package for making working with tables between Rmarkdown and Tex easier.

This cost some adjustment to the Tex templates to make it work, but it now works nicely.

See documentation for this package [here](https://hughjonesd.github.io/huxtable/huxtable.html). A particularly nice addition of this package is for making the printing of regression results a joy (see [here](https://hughjonesd.github.io/huxtable/huxtable.html#creating-a-regression-table)). Here follows an example:


If you are eager to use huxtable, comment out the Huxtable table in the Rmd template, and uncomment the colortbl package in your Rmd's root.

Note that I do not include this in the ordinary template, as some latex users have complained it breaks when they build their Rmds (especially those using tidytex - I don't have this problem as I have the full Miktex installed on mine). Up to you, but I strongly recommend installing the package manually and using huxtable. To make this work, uncomment the _Adding additional latex packages_ part in yaml at the top of the Rmd file. Then comment out the huxtable example in the template below this line. Reknit, and enjoy.

```{r, results = 'asis'}
list.files('code/', full.names = T, recursive = T) %>% as.list() %>% walk(~source(.))
if(!require(huxtable)) install.packages(huxtable)
library(huxtable)
data(diamonds, package = 'ggplot2')
Title <- "Regression Output"
Label <- "Reg01"
lm1 <- lm(price ~ carat, diamonds)
lm2 <- lm(price ~ depth, diamonds)
lm3 <- lm(price ~ carat + depth, diamonds)
htab <-
huxreg(lm1, lm2, lm3,
                statistics = c(N = "nobs", R2 = "r.squared"),
                note = "%stars%.") %>%
  set_caption(Title) %>%
  set_label(Label)
# More settings:
font_size(htab) <- 12
# Let's change regression names: this is slightly hacky, but works. Comment out this section to see what the default looks like:
  Names <- c( "Reg1", "Reg2", "Reg3")
  for(i in 1:length(Names)) {
    htab[1,][[1+i]] <- Names[i]
  }
# Now simply call the table:
htab

```

FYI - R also recently introduced the gt package, which is worthwhile exploring too.

# Lists

To add lists, simply using the following notation

* This is really simple

    + Just note the spaces here - writing in R you have to sometimes be pedantic about spaces...

* Note that Rmarkdown notation removes the pain of defining \LaTeX environments!

# Conclusion

I hope you find this template useful. Remember, stackoverflow is your friend - use it to find answers to questions. Feel free to write me a mail if you have any questions regarding the use of this package. To cite this package, simply type citation("Texevier") in Rstudio to get the citation for @Texevier (Note that uncited references in your bibtex file will not be included in References).

<!-- Make title of bibliography here: -->
<!-- \newpage -->

\newpage

# References {-}

<div id="refs"></div>


# Appendix {-}

## Appendix A {-}

Some appendix information here

## Appendix B {-}

